Visually pleasing knot projections

### 2021-09-16 inst/jma_knot.tex
fixes #29

Many of the knots in Figure~\ref{knot_table} have an axis of symmetry,
or possess rotational symmetry.  The package has the ability to impose
symmetry relations on knots, and to optimize the resulting symmetrical
knot.  Minimizing the badness is not entirely straightforward on
account of the induced redundancy, which is characterized using a
symmetry object specific to the knot under consideration.  However,
symmetry constraints do reduce the dimensionality of the optimization
problem.

>>>>

Many of the knots in Figure~\ref{knot_table} have an axis of symmetry,
or possess rotational symmetry; some have both and thus have a
dihedral symmetry group.  The package has the ability to impose these
symmetry relations on knots, and to optimize the resulting symmetrical
knot.  Minimizing the badness is not entirely straightforward on
account of the induced redundancy, which is characterized using a
symmetry object specific to the knot under consideration.  However,
symmetry constraints do reduce the dimensionality of the optimization
problem.
